\textcolor{Navy}{\textsc{Convexity adjustments with a bit of Malliavin}}

### 2022-12-03 Latex/paper.tex
# new approach to cms mc

We suppose, that we have a flow in $T_a < T_p < T_b$ with value $S_{a,b}(T_a)$. Then, the present value of this flow under the differents measure $\mathbb{Q}^{T_a}$,$\mathbb{Q}^{01(a,b)}$ and $\mathbb{Q}^{T_p}$ respectivaly is 
\begin{align}\label{cms_expedted_value}
P_{ois}(0,T_a)\mathbb{E}^{\mathbb{Q}^{T_{a}}}\left(S_{a,b}(T_a) P_{ois}(T_a,T_p) \right) &= 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \frac{P_{ois}(T_a,T_p)}{01(T_a,T_a,T_b) }\right) \nonumber \\
&= 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) M(T_a,T_p)\right) \\
&=P_{ois}(0,T_p)\mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right)
\end{align}
where $M(t, T_p)= \frac{P_{ois}(t,T_p) }{01(t,T_a,T_b)} $. From the definition of $S_{a,b}(t)$ and $S^{ois}_{a,b}(t)$, we have that both are martingale under the measure $\mathbb{Q}^{01(a,b)}$. Therefore, we will define the convexity adjustment for CMS the next  way
\begin{equation*}
CA_{cms}(T_0,T_p) = S_{a,b}(0) - \mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right). 
\end{equation*}
We will follow the same strategy that in the last examples. From Clark-Ocone formula we have that
\begin{equation*}
S_{a,b}(T_a) = \mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right) + \int_{0}^{T_a} \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) dW^{T_p}_s 
\end{equation*} 
Therefore, if we take $\mathbb{E}^{01(a,b)}$ and we use the Girsanov theorem  in the last expression, we get 
\begin{equation*}
S_{a,b}(0) = \mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right) + \frac{01(0,T_a,T_b)}{P_{ois}(0,T_p)} \mathbb{E}^{T_p}\left(M(T_a,T_p) \int_{0}^{T_a} \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) dW^{T_p}_s \right)
\end{equation*}
Now, if we use that the Skorohod integral is the adjoint operator of the Malliavin derivative, we have that
\begin{align*}
S_{a,b}(0) &= \mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right) + \frac{01(0,T_a,T_b)}{P_{ois}(0,T_p)} \mathbb{E}^{T_p}\left(\int_{0}^{T_a} D_s M(T_a,T_p) \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) ds  \right) \\
&=\mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right) + \frac{01(0,T_a,T_b)}{P_{ois}(0,T_p)} \mathbb{E}^{T_p}\left(\int_{0}^{T_a} \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s M(T_a,T_p)\right) \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) ds  \right).
\end{align*}
Then we have the next expression for the convexity adjustment
\begin{equation*}
CA_{cms}(T_0,T_p) = \frac{01(0,T_a,T_b)}{P_{ois}(0,T_p)} \mathbb{E}^{T_p}\left(\int_{0}^{T_a} \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s M(T_a,T_p)\right) \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) ds  \right).
\end{equation*}
Now, if we do a freeze of $\partial_x M(t,T_p)$ and $\partial_x S_{a,b}(t)$, then we can do the next approximation for $CA_{ois}(T_0,T_p)$
\begin{align*}
CA_{cms}(T_0,T_p) &=  \frac{01(0,T_a,T_b)}{P_{ois}(0,T_p)} \mathbb{E}^{T_p}\left(\int_{0}^{T_a} \mathbb{E}^{T_p}_s \left(\partial_x M(T_a,T_p) D_s x_{T_a}\right) \mathbb{E}^{T_p}_s \left(\partial_x S_{a,b}(T_a)D_s x_{T_a} \right) ds \right) \\
& \approx \frac{01(0,T_a,T_b)}{P_{ois}(0,T_p)} \partial_x M(T_a,T_p, x_0, y_0)  \partial_x S_{a,b}(T_a,x_0,y_0) \mathbb{E}^{\mathbb{Q}^{T_p}}\left(\int_{0}^{T_a} \left(D_s x_{T_a} \right)^{2} ds \right).
\end{align*}
Now, if we use (\ref{approximation_D_s_x_t}) we can estimate  
$
 \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(\left(D_s x_{T_a} \right)^{2}\right)
$
the next way 
\begin{align*} 
\mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(\left(D_s x_{T_a} \right)^{2}\right) &\approx \exp\left(-2 \int_{s}^{T_a}k_u du \right) \eta^{2}(s,\bar{x}_0,\bar{y}_{T_a}) \\
& \cdot \exp\left(\int_{s}^{T_a} \left(\partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a})\right)^{2} - 2 \exp\left(-\int_{s}^{T_a}k_u du\right) \partial_x (\bar{\nu}(u,T_a) \bar{\nu}(u,T_p)) \right) du
\end{align*}
Therefore, we have that
\begin{align*}
CA_{cms}(T_0,T_p) &\approx 
\end{align*}

\begin{example}
In the case of a Hull-White model, we showed in the example  (\ref{example_convexity_hw_ois}) that 
$$
\eta(t,x_t, y_t) = \sigma\exp(-kt)
$$
\end{example}
Therefore (\ref{cms_adjustment}) is reduced to
\begin{equation}\label{hullwhite_cms_convexity}
01(0,T_a,T_b)  f^{\prime}(S^{ois}_{a,b}(T_a)) \partial_{x}S_{a,b}(0,\bar{x}_0, \bar{y}({T_a}) \partial_{x}S^{ois}_{a,b}(0,\bar{x}_0, \bar{y}({T_a}) \frac{ \sigma^2(1-\exp(-2kT_a))}{2k} 
\end{equation}
A common practice in market, it is suppose that $f(x)=\alpha x + \beta$ (TSR model). We must to impose two equations in order to get $\alpha$ and $\beta$. The first equation follows straightforward from the definition of $M(t,T_p)$. Since, $M(t,T_p)$ is a $01(a,b)-$martingale we must have that
\begin{equation*}
\mathbb{E}^{01(a,b)}\left(\alpha S^{ois}_{a,b}(T_a) + \beta \right) = \frac{P_{ois}(0,T_p)}{01(0,T_a,T_b)}.
\end{equation*}
Therefore
\begin{equation*}
\beta = \frac{P_{ois}(0,T_p)}{01(0,T_a,T_b,x_0,y_0)} - \alpha S^{ois}_{a,b}(0,x_0,y_0).
\end{equation*}
Under a separable HJM dynamic we must have that
\begin{equation*}
\alpha \partial_{x} S^{ois}_{a,b}(0) = - M(0,T_p)\left(G(T_a,T_p)+\frac{\partial_x 01(0,T_a,T_b)}{01(0,T_a,T_b)}\right).
\end{equation*}
Then
\begin{equation*}
\alpha = -\frac{M(0,T_p)\left(G(T_a,T_p)+\frac{\partial_x 01(0,T_a,T_b)}{01(0,T_a,T_b)}\right)}{\partial_{x} S^{ois}_{a,b}(0)}.
\end{equation*}
Then from the last equalities, we can approximate the convexity adjustment of a CMS rate as
\begin{align*}
&CA_{CMS}(T_a,T_b) \\ 
\approx& \alpha 01(0,T_a,T_b) \partial_{x}S_{a,b}(0,\bar{x}_0, \bar{y}({T_a}) \partial_{x}S^{ois}_{a,b}(0,\bar{x}_0, \bar{y}({T_a}) \frac{ \sigma^2(1-\exp(-2kT_a))}{2k}  \\   
=& - P_{ois}(0,T_p) \left(G(T_a,T_p)+\frac{\partial_x 01(0,T_a,T_b)}{01(0,T_a,T_b)}\right) \partial_{x}S_{a,b}(0,\bar{x}_0, \bar{y}({T_a})) \frac{S^{ois}_{a,b}(0,\bar{x}_0, \bar{y}({T_a}))}{S^{ois}_{a,b}(0)}  \frac{ \sigma^2(1-\exp(-2kT_a))}{2k}
\end{align*}
In the next figure, we can see the convexity adjustment for a CMS where the tenor for the underlying swap is 5Y using the last approximation and Monte Carlo method

>>>>

We suppose, that we have a flow in $T_a < T_p < T_b$ with value $S_{a,b}(T_a)$. Then, the present value of this flow under the differents measure $\mathbb{Q}^{T_a}$,$\mathbb{Q}^{01(a,b)}$ and $\mathbb{Q}^{T_p}$ respectivaly is 
\begin{align}\label{cms_expedted_value}
P_{ois}(0,T_a)\mathbb{E}^{\mathbb{Q}^{T_{a}}}\left(S_{a,b}(T_a) P_{ois}(T_a,T_p) \right) &= 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \frac{P_{ois}(T_a,T_p)}{01(T_a,T_a,T_b) }\right) \nonumber \\
&= 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) M(T_a,T_p)\right) \\
&=P_{ois}(0,T_p)\mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right)
\end{align}
where $M(t, T_p)= \frac{P_{ois}(t,T_p) }{01(t,T_a,T_b)} $. From the definition of $S_{a,b}(t)$ and $S^{ois}_{a,b}(t)$, we have that both are martingale under the measure $\mathbb{Q}^{01(a,b)}$. Therefore, we will define the convexity adjustment for CMS the next  way
\begin{equation*}
CA_{cms}(T_0,T_p) = S_{a,b}(0) - \mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right). 
\end{equation*}
We will follow the same strategy that in the last examples. From Clark-Ocone formula we have that
\begin{equation*}
S_{a,b}(T_a) = \mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right) + \int_{0}^{T_a} \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) dW^{T_p}_s 
\end{equation*} 
Therefore, if we take $\mathbb{E}^{01(a,b)}$ and we use the Girsanov theorem  in the last expression, we get 
\begin{equation*}
S_{a,b}(0) = \mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right) + M(0,T_p) \mathbb{E}^{T_p}\left( \frac{1}{M(T_a,T_p)} \int_{0}^{T_a} \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) dW^{T_p}_s \right)
\end{equation*}
Now, if we use that the Skorohod integral is the adjoint operator of the Malliavin derivative, we have that
\begin{align*}
S_{a,b}(0) &= \mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right) + M(0,T_p) \mathbb{E}^{T_p}\left(\int_{0}^{T_a} D_s \left(\frac{1}{M(T_a,T_p)} \right) \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) ds  \right) \\
&=\mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right) + M(0,T_p) \mathbb{E}^{T_p}\left(\int_{0}^{T_a} \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(\frac{1}{M(T_a,T_p)} \right) \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) ds  \right).
\end{align*}
Then we have the next expression for the convexity adjustment
\begin{equation*}
CA_{cms}(T_0,T_p) = - \frac{01(0,T_a,T_b)}{P_{ois}(0,T_p)} \mathbb{E}^{T_p}\left(\int_{0}^{T_a} \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s \left(\frac{1}{M(T_a,T_p)}\right)\right) \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) ds  \right).
\end{equation*}
Now, if we do a freeze of $\partial_x M(t,T_p)$ and $\partial_x S_{a,b}(t)$, then we can do the next approximation for $CA_{ois}(T_0,T_p)$
\begin{align*}
CA_{cms}(T_0,T_p) &=  - M(0,T_p) \mathbb{E}^{T_p}\left(\int_{0}^{T_a} \mathbb{E}^{T_p}_s \left(\partial_x \left(\frac{1}{M(T_a,T_p)}\right) D_s x_{T_a}\right) \mathbb{E}^{T_p}_s \left(\partial_x S_{a,b}(T_a)D_s x_{T_a} \right) ds \right) \\
& \approx c \frac{ \partial_x M(T_a,T_p, x_0, y_0)}{M(T_a,T_p, x_0, y_0)}  \partial_x S^{ois}_{a,b}(T_a,x_0,y_0) \mathbb{E}^{\mathbb{Q}^{T_p}}\left(\int_{0}^{T_a} \left(D_s x_{T_a} \right)^{2} ds \right).
\end{align*}
with $c = \frac{S_{a,b}(0)}{S^{ois}_{a,b}(0)}$. Now, if we use (\ref{approximation_D_s_x_t}) we can estimate  
$
 \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(\left(D_s x_{T_a} \right)^{2}\right)
$
the next way 
\begin{align*} 
\mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(\left(D_s x_{T_a} \right)^{2}\right) &\approx \exp\left(-2 \int_{s}^{T_a}k_u du \right) \eta^{2}(s,\bar{x}_0,\bar{y}_{T_a}) \\
& \cdot \exp\left(\int_{s}^{T_a} \left(\partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a})\right)^{2} - 2 \exp\left(-\int_{s}^{T_a}k_u du\right) \partial_x (\bar{\nu}(u,T_a) \bar{\nu}(u,T_p)) \right) du
\end{align*}
Therefore, we have that
\begin{align*}
CA_{cms}(T_0,T_p) &\approx 
\end{align*}

\begin{example}
In the case of a Hull-White model, we showed  in (\ref{example_convexity_hw_ois}) that 
$$
\eta(t,x_t, y_t) = \sigma\exp(-kt)
$$
and
$$
D_s x_{T_a} = \sigma \exp(-(T_a - s))
$$
and therefore, we have that
\begin{equation*}
\mathbb{E}^{\mathbb{Q}^{T_p}}\left(\int_{0}^{T_a}(D_s x_{T_a})^{2} ds \right) = \sigma^{2} \frac{1 - \exp(-2kT_a)}{2k}.
\end{equation*}

In the next figure, we can see the convexity adjustment for a CMS where the tenor for the underlying swap is 5Y using the last approximation and Monte Carlo method
\end{example}
